---
title: "Missingness Imputation"
author: "Yiran Qin"
output: html_notebook
---

```{r}
library(quantmod)
library(magrittr)
```

```{r}
start <- as.Date("2020-03-01")
end <- as.Date("2020-06-02")
```

According to the assignment requirements on the slides, I need to get Dow Jones index and 10 more companies data. Since they all used abbreviations on Yahoo finance, I will write their names down here. They are Apple, Goldman Sachs, Microsoft, Snapchat, Boeing, Google, Amazon, JP Morgan Chase, Alibaba and Nike.

```{r}
getSymbols(c("^DJI", "AAPL", "GS", "MSFT", "SNAP", "BA", "GOOG", "AMZN", "JPM", "BABA", "NKE"), src = "yahoo", from = start, to = end)
```

```{r}
stocks <- as.xts(data.frame(DJI = DJI[, "DJI.Close"], AAPL = AAPL[, "AAPL.Close"], GS = GS[, "GS.Close"], MSFT = MSFT[, "MSFT.Close"], SNAP = SNAP[, "SNAP.Close"], BA = BA[, "BA.Close"], GOOG = GOOG[, "GOOG.Close"], AMZN = AMZN[, "AMZN.Close"], JPM = JPM[, "JPM.Close"], BABA = BABA[, "BABA.Close"], NKE = NKE[, "NKE.Close"]))
```

The reason why the Date begins with '2020-03-02' because '2020-03-01' is a Saturday, stock market closes on weekends, holidays and meltdown.I think this also the part of the reason we need to find out missing data.            
```{r}
head(stocks)
```

```{r}

```

