---
title: "Stock Market with quantmod"
author: "Yiran Qin"
output:
  html_notebook: default
  pdf_document: default
---

For this R Notebook, I will follow the tutorial and create a visualization plot for Facebook, and we are going to compare the stock prices change for few other companies.

```{r}
library(quantmod)
library(magrittr)
```

```{r}
start <- as.Date("2020-02-01")
end <- as.Date("2020-06-01")
getSymbols("FB", src = "yahoo", from = start, to = end)
```

```{r}
class(FB)
```

```{r}
head(FB)
```

Next we need to visualize the dataset

```{r}
plot(FB[, "FB.Close"], main = "FB")
```

Scatter plot is fine but financial data is often plotted by a Japanese candlestick plot, here we go:

```{r}
candleChart(FB, up.col = "green", dn.col = "blue", theme = "white")
```
Then we can compare with other famous companies in the US. For instance, Boeing, Google and Amazon.

```{r}
getSymbols(c("BA", "GOOG", "AMZN"), src = "yahoo", from = start, to = end)
```

```{r}
stocks <- as.xts(data.frame(FB = FB[, "FB.Close"], BA = BA[, "BA.Close"], GOOG = GOOG[, "GOOG.Close"], AMZN = AMZN[, "AMZN.Close"]))
```


```{r}
head(stocks)
```

```{r}
plot(as.zoo(stocks[, c("FB.Close", "BA.Close")]), screens = 1, lty = 1:2, 
    xlab = "Date", ylab = "Price")
par(new = TRUE)
plot(as.zoo(stocks[, "GOOG.Close"]), screens = 1, lty = 3, xaxt = "n", yaxt = "n", 
    xlab = "", ylab = "")
plot(as.zoo(stocks[, "AMZN.Close"]), screens = 1, lty = 3, xaxt = "n", yaxt = "n", 
    xlab = "", ylab = "")
axis(4)
mtext("Price", side = 4, line = 3)
legend("topleft", c("FB (left)", "BA (left)", "GOOG", "AMZN"), lty = 1:3, cex = 0.5)
```
Due to Google's stock prices are way too higher than others, so R creates another graph for Google.

```{r}
stock_return = apply(stocks, 1, function(x) {x / stocks[1,]}) %>% 
                                    t %>% as.xts

head(stock_return)
```

```{r}
plot(as.zoo(stock_return), screens = 1, lty = 1:3, xlab = "Date", ylab = "Return")
legend("topleft", c("FB", "BA", "GOOG", "AMZN"), lty = 1:3, cex = 0.5)
```

